### 2016-08-30 version0.0/intro0.01.tex
Applying R.A.'s comments on the intro

\section{Prelude}
\label{sec: overview}
%what doIhave inside galaxies:
% stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are billions of stars, planets, and black holes, as well as dust and gas.
They all affect each others' formation, evolution, and extinction.
There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their electromagnetic radiation.
Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
Therefore, with proper modeling of observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.

%stars
Arguably, stars are the main component of normal galaxies.
They control the chemical composition and structure of galaxies by transforming gas into new stars and by transforming dead stars back into gas.
They are also central to the formation and evolution of planetary systems.
The energy provided by stars is necessary to create and maintain the life on planets. 
The study of the formation and evolution of the Sun, and more generally that of stars, helps us understand more about our origin and the future of our Solar System.
Furthermore, in order to completely understand the formation and evolution of galaxies from the early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary. 
As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.

@@

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
The stellar population synthesis method, which sums stellar spectra to produce a composite spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minimizing $\chi^2$ or by Bayesian analysis), using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see][for more detail]{Walcher08}.
For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
By integrating star formation history over a specific time scale, SFR can be derived.
Knowing the stellar mass to light ratio, one can use a galaxy's observed luminosity to calculate its stellar mass.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically proven that they have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

>>>>

\section{Prelude}
\label{sec: overview}
%what doIhave inside galaxies:
% stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are billions of stars, planets, and black holes, as well as dust and gas.
They all affect each others' formation, evolution, and extinction.
There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their electromagnetic radiation.
Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool for understanding galaxies. 
Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
Therefore, by properly modeling of observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.

%stars
Arguably, stars are the main component of normal galaxies.
They control the chemical composition and structure of galaxies by transforming gas into new stars and by transforming dead stars back into gas.
They are also central to the formation and evolution of planetary systems.
The energy provided by stars is necessary to create and maintain the life on planets. 
The study of the formation and evolution of the Sun, and more generally that of stars, helps us understand more about our origin and the future of our Solar System.
Furthermore, in order to completely understand the formation and evolution of galaxies from the early universe to the current epoch, knowledge of the formation and evolution of stars is necessary. 
As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.

@@

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
The stellar population synthesis method, which sums stellar spectra to produce a composite spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minimizing $\chi^2$ or by Bayesian analysis), using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see][for more detail]{Walcher08}.
For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
By integrating instantaneous star formation over a specific time scale, SFR can be derived.
Knowing the stellar mass to light ratio, one can use a galaxy's observed luminosity to calculate its stellar mass.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically proven that they have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\citep{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).
